\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-08 casestudies.tex
add one sentence about parser case study

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
the two abstract interpreters in \lsti{ImpTI} and \lsti{ImpCP} are
directly runnable in Coq.
We also extract them to OCaml and put them to test over simple queries.

@@

>>>>

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
the two abstract interpreters in \lsti{ImpTI} and \lsti{ImpCP} are
directly runnable in Coq.
We also extract them to OCaml and put them to test over queries.

@@

In addition to the two case studies above, we also use extensible
inductive types for modeling extensible context-free grammars and derive
decision procedures for them.
